---
title: "Rcode_Batteryproj_rmd"
author: "Qibin"
date: "24/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())

```

## Data Download
```{r}
year <- 2015
for(month in c(1:12)){
filename <- sprintf("PRICE_AND_DEMAND_%4d%02d_NSW1.csv",year,month)
download.file(paste0('https://www.aemo.com.au/aemo/data/nem/priceanddemand/',filename),
              paste0('Price_and_Demand/',filename))
}
              
              
#dat<-read.csv('Price_and_Demand/PRICE_AND_DEMAND_202006_NSW1.csv')
```


## Data Import

```{r}

filename<- sprintf("Price_and_Demand/PRICE_AND_DEMAND_2017%02d_NSW1.csv",1)
data2017 <- read.csv(filename)
for(i in c(2:12)){
  filename<- sprintf("Price_and_Demand/PRICE_AND_DEMAND_2017%02d_NSW1.csv",i)
  datatemp <- read.csv(filename)
  data2017<- rbind(data2017,datatemp)
  rm(datatemp)
}
saveRDS(data2017,"data2017.rds")


filename<- sprintf("PRICE_AND_DEMAND_2018%02d_NSW1.csv",1)
data2018 <- read.csv(filename)
for(i in c(2:12)){
  filename<- sprintf("PRICE_AND_DEMAND_2018%02d_NSW1.csv",i)
  datatemp <- read.csv(filename)
  data2018<- rbind(data2018,datatemp)
  rm(datatemp)
}

filename<- sprintf("PRICE_AND_DEMAND_2019%02d_NSW1.csv",1)
data2019 <- read.csv(filename)
for(i in c(2:12)){
  filename<- sprintf("PRICE_AND_DEMAND_2019%02d_NSW1.csv",i)
  datatemp <- read.csv(filename)
  data2019<- rbind(data2019,datatemp)
  rm(datatemp)
}

filename<- sprintf("PRICE_AND_DEMAND_2020%02d_NSW1.csv",1)
data2020 <- read.csv(filename)
for(i in c(2:9)){
  filename<- sprintf("PRICE_AND_DEMAND_2020%02d_NSW1.csv",i)
  datatemp <- read.csv(filename)
  data2020<- rbind(data2020,datatemp)
  rm(datatemp)
}

#saveRDS(data2018,"data2018.rds")
#saveRDS(data2019,"data2019.rds")
#saveRDS(data2020,"data2020.rds")

```

RRP refers to the average spot price ($/MWh) per region for each day, and PEAK RRP refers to the average peak price from 7:00am to 10:00pm EST. 


```{r}

sum(data2017$TOTALDEMAND*data2017$RRP)/sum(data2017$TOTALDEMAND)

sum(data2018$TOTALDEMAND*data2018$RRP)/sum(data2018$TOTALDEMAND)

sum(data2019$TOTALDEMAND*data2019$RRP)/sum(data2019$TOTALDEMAND)

sum(data2020$TOTALDEMAND*data2020$RRP)/sum(data2020$TOTALDEMAND)

range(data2018$RRP)
range(data2019$RRP)
range(data2020$RRP)

mean(data2018$RRP)
mean(data2019$RRP)
mean(data2020$RRP)
```



```{r}
## import the NSW electric load data in Feburary, 2019

DataSet1<-readRDS("data2018.rds")

## import the NSW electric load data in March, 2019

DataSet2<-readRDS("data2019.rds")

```



## Model with Battery
### Model Framework

This is the frame of Asymmetric SVR regression model + Asymmetric epsilon.
```{r}
####################################################
###### Asymmetric SVR regression model + Asymmetric epsilon#####
####################################################

# k2 is for under-prediction and k1 is for over prediction 

# AsySVR_2 is the loss function
AsySVR_2<-function(beta, TrainX, TrainY, k1, k2, Const, cap, stp)
  
{
  eps1 <- cap*stp
  eps2 <- cap-eps1
  beta<-array(beta)
  TrainX_extra<-rep(1, times=dim(TrainX)[1])
  TrainX<-cbind(TrainX_extra,TrainX)
  Xmatrix<-as.matrix(TrainX)
  Err<-Xmatrix %*% beta-TrainY
  # under-ordered, error cost k1, eps1
  InsenErr1<- ifelse(Err< -eps1,-k1*(Err+eps1),0)
  # over-ordered, error cost k2, eps2,  
  InsenErr2<- ifelse(Err> eps2, k2*(Err-eps2), 0)
  
  SampleLLC<-InsenErr1+InsenErr2
  #rentC <- pcost*cap*nrow(TrainX)
  L2<-sum((beta[2:dim(TrainX)[2]])^2)
  TrainLLC<- L2+Const*(sum(SampleLLC))
}
#AsySVR_2_ecost returns the daily prediction error loss
AsySVR_2_ecost <- function(beta, TrainX, TrainY, k1, k2, Const, cap, stp){
  eps1 <- cap*stp
  eps2 <- cap-eps1
  beta<-array(beta)
  TrainX_extra<-rep(1, times=dim(TrainX)[1])
  TrainX<-cbind(TrainX_extra,TrainX)
  Xmatrix<-as.matrix(TrainX)
  Err<-Xmatrix %*% beta-TrainY
  # under-ordered, error cost k1, eps1
  InsenErr1<- ifelse(Err< -eps1,-k1*(Err+eps1),0)
  # over-ordered, error cost k2, eps2,  
  InsenErr2<- ifelse(Err> eps2, k2*(Err-eps2), 0)
  
  SampleLLC<-InsenErr1+InsenErr2
  #rentC <- pcost*cap
  TrainLLC<- (mean(SampleLLC))*48 #MDC daily cost
          
}

```


### Cross-Validation (CV) Results
The CV results (data_cv) was run from HPC. 

R file battery_hpc_cv5_2.R generates data, where dataset have four columns as follows.

"ConstantC"       "Capacity"        "Storage"         "Ecnomic_cost_Tr"

```{r}

opt_cap <- function(a,b,p){
  output <- matrix(0,length(a),length(p))
  for(i in c(1:length(p))){
    output[,i] <- (log(-p[i]/a)-b)/a
  }
  output
} 

pcost <- c(seq(1,75,1))*48

idd <- 3 # for idd  = 1,2,3 from k2 = 70

k2<- c(70,80,90)[idd]
k1<- c(400,600,800)#,"realtime")
constantC <- c(1,10,100)
tt <- 1
outpout_ab_p <- as.data.frame(matrix(0,9,6+length(pcost))) ##was 12, was 71

output_data <- c()
output_pred <- c()


for(i in 1:3){ #k1

  for(j in 1:3){ #C
    
    dataname<- paste0("data_cv/k1_",k2,"_k2_",k1[i],"_",constantC[j],"_cv.rds")
    res<- readRDS(dataname)
    names(res)<-c("ConstantC","Capacity","Storage","Ecnomic_cost_Tr")

    av_stp <- aggregate(x = res$Ecnomic_cost_Tr,                # Specify data column
                        by = list(res$Capacity),              # Specify group indicator
                        FUN = min) 
    names(av_stp) <-c("Capacity","Ecnomic_cost_Tr")
    
    mn_stp <- aggregate(x = res$Ecnomic_cost_Tr,                # Specify data column
                        by = list(res$ConstantC,res$Capacity),              # Specify group indicator
                        FUN = min) 
    
    fo2 <- Ecnomic_cost_Tr ~ exp(b + a * Capacity)
    fm2 <- summary(nls(fo2, av_stp, start = list(a = -0, b = 13),algorithm = "port"))
    
    fo3 <- Ecnomic_cost_Tr ~ a*(Capacity-b)^2
    fm3 <- summary(nls(fo3, av_stp, start = list(a = 0.01, b = 2500),algorithm = "port"))
    
    optcap<-opt_cap(fm2$coefficients[1,1],fm2$coefficients[2,1],pcost)

    outpout_ab_p[tt,1] <- k2
    outpout_ab_p[tt,2] <- k1[i]
    outpout_ab_p[tt,3] <- constantC[j]
    outpout_ab_p[tt,4] <- fm2$coefficients[1,1]
    outpout_ab_p[tt,5] <- fm2$coefficients[2,1]
    outpout_ab_p[tt,6:(length(pcost)+5)] <- optcap
    
    tt<- tt+1
    preidct.val <- exp(fm2$coefficients[2,1] +fm2$coefficients[1,1]* 10^seq(0,3,0.1))
    #plot(av_stp$Capacity,av_stp$Ecnomic_cost_Tr,ylab="Economic cost (training)",col=1)
    #lines(10^seq(0,3,0.1),preidct.val)
    
    temdata <- c(k2,k1[i],constantC[j],av_stp$Ecnomic_cost_Tr)
    tempred <-c(k2,k1[i],constantC[j],preidct.val)
    
    output_data <- rbind(output_data,temdata)
    output_pred <- rbind(output_pred,tempred)
  }
  
}

#names(outpout_ab_p)
#otimalc
data.optC <- data.frame()
for (row.id in 1:nrow(outpout_ab_p)){
  temp<-cbind(as.data.frame(matrix(outpout_ab_p[row.id,1:5],75,5,byrow = TRUE)),
    cbind(t(outpout_ab_p[row.id,6:80]),seq(1,75,1)))
  names(temp) <- c("k2","k1","ConstC","a","b","Cap","Pcost")
  data.optC <- rbind(data.optC,temp)
}

data.optC <- data.optC[which(data.optC$Cap>1),]
data.optC$Cap <- round(data.optC$Cap,digits = 0)
filename.data.optC <- paste0("data_cv/k1_1_75",k2,"_data_optC.rds")
#saveRDS(data.optC,filename.data.optC)

```

```{r,plot Prediction error cost vs Battery capacity,bymm,year}

  dataobs.1 <- output_data[2,4:22]
  dataobs.2 <- output_data[5,4:22]
  dataobs.3 <- output_data[8,4:22]
  xobs <- c(1,5,10,20,40,60,80,100,150,200,250,300,400,500,600,700,800,900,1000)
  datapred.1 <- output_pred[2,4:34]
  datapred.2 <- output_pred[5,4:34]
  datapred.3 <- output_pred[8,4:34]
  xpred<- 10^seq(0,3,0.1)
  
  
  my <- 10^6/365
  pdf(file = paste0("figure_costcurvek1_",k2,"_mm.pdf"),height = 4.5, width = 5 )
  plot(xpred,datapred.1/my,type = "l",col = 1,lwd=2.5,ylim = c(0,0.8*365),xlab = "Battery capacity (MV)", ylab = "Prediction error cost (AUD$MM)")
  points(xobs,dataobs.1/my,col=1)
  
  lines(xpred,datapred.2/my,col = 2,lwd=2.5)
  points(xobs,dataobs.2/my,col = 2)
  
  lines(xpred,datapred.3/my,col = 3,lwd=2.5)
  points(xobs,dataobs.3/my,col = 3)
  
  legend(600, 0.7*365, legend=c(paste0("k1=400,","k2=",k2), paste0("k1=600,","k2=",k2),paste0("k1=800,","k2=",k2)),
       col=c(1, 2,3), lty=1,lwd = 2.5, cex=0.8)

  dev.off()
  
```


```{r, same figure}
  
  datapred.1 <- output_pred[2,4:34]
  datapred.2 <- output_pred[5,4:34]
  datapred.3 <- output_pred[8,4:34]
  xpred<- 10^seq(0,3,0.1)
  
  pdf(file = paste0("figure_costcurvek1_",k2,".pdf"),height = 4.5, width = 5 )
  plot(xpred,datapred.1/10^5,type = "l",col = 1,lwd=2.5,ylim = c(0,8),xlab = "Battery capacity (MV)", ylab = "Prediction error cost (AUD$ 100,000)")
  points(xobs,dataobs.1/10^5,col=1)
  
  lines(xpred,datapred.2/10^5,col = 2,lwd=2.5)
  points(xobs,dataobs.2/10^5,col = 2)
  
  lines(xpred,datapred.3/10^5,col = 3,lwd=2.5)
  points(xobs,dataobs.3/10^5,col = 3)
  
 legend(600, 0.7*365, legend=c(paste0("k1=400,","k2=",k2), paste0("k1=600,","k2=",k2),paste0("k1=800,","k2=",k2)),
       col=c(1, 2,3), lty=1,lwd = 2.5, cex=0.8)

  dev.off()
  
  


```

```{r,figure battery capacity - annual gain}
train_error_cost<- matrix(data = c(469004.3, 588401.9, 679707.6,  511689.8, 627772.5, 725395.0, 541779.7, 665547.5, 769381.0),nrow = 3, ncol = 3, byrow = TRUE)

  mypcost <- c(seq(0.1,0.9,by = 0.1)*48,pcost)

  optimal_cap <- opt_cap(-0.002512378,13.05937,mypcost) # k1=400, k2=70
  optimal_cap<-optimal_cap[which(optimal_cap>0)]
  pcost_cap <- mypcost[which(optimal_cap>0)]#seq(1,length(optimal_cap),by = 1)*48
  optcost_cap<-469004.3 - exp( 13.05937 -0.002512378* optimal_cap) - optimal_cap*pcost_cap
  
  total_gain <-function(mycap,pcost){
    (469004.3 - exp( 13.05937 -0.002512378* mycap) - mycap*pcost)/my
  }
  

datapred.1 <- output_pred[2,4:34]
  datapred.2 <- output_pred[5,4:34]
  datapred.3 <- output_pred[8,4:34]
  xpred<- seq(0,2000,10)#10^seq(0,3,0.1)
  
  xpred0 <-c(0,xpred)

  pcost1 <- xpred0*1*48/my
  pcost5 <- xpred0*5*48/my
  pcost10 <- xpred0*10*48/my
  pcost15 <- xpred0*15*48/my
  pcost20 <- xpred0*20*48/my
  
  pdf(file = paste0("figure_pcost_mm.pdf"),height = 4.5, width = 5 )
  gain1 <-c(0,(train_error_cost[idd,1]-datapred.1)/my)
  plot(xpred0,pcost1,type='l',lwd=2,col=1,ylim = c(0,0.45*365),xlim=c(-10,2300), xlab= "Battery capacity (MV)",ylab = "Battery annual cost (AUD $MM)")
  lines(xpred0,pcost5, col=2,lwd=2)
  lines(xpred0,pcost10, col=3,lwd=2)
  lines(xpred0,pcost15, col=4,lwd=2)
  lines(xpred0,pcost20, col=5,lwd=2)
  #lines(xpred,pcost25, col=4)
  legend(1600, 0.28*365, legend=c("p = 1","p = 5","p = 10","p = 15","p = 20"),col=c(1, 2,3, 4,5), lty=1,lwd = 2.5, cex=0.75)
  dev.off()
  #70
  pdf(file = paste0("figure_gain_size_",70,"_.pdf"),height = 4.5, width = 5 )
  plot(xpred,total_gain(xpred,1*48), type='l',lwd=2,col = 1, xlab = "Battery capacity (MV)", ylab= "Annual gain (AUD $MM)",ylim=c(0,0.45*365),xlim=c(-10,2300))
   lines(xpred,total_gain(xpred,5*48), col = 2,lwd=2 )
  lines(xpred,total_gain(xpred,10*48), col = 3,lwd=2 )
  lines(xpred,total_gain(xpred,15*48), col = 4,lwd=2 )
  lines(xpred,total_gain(xpred,20*48), col = 5,lwd=2 )
  
  lines(c(opt_cap(-0.002512378,13.05937,1*48),opt_cap(-0.002512378,13.05937,1*48)),
        c(0,total_gain(opt_cap(-0.002512378,13.05937,1*48),1*48)),col = 1,lty = 2)
  
  lines(c(opt_cap(-0.002512378,13.05937,5*48),opt_cap(-0.002512378,13.05937,5*48)),
        c(0,total_gain(opt_cap(-0.002512378,13.05937,5*48),5*48)),col = 2,lty = 2)
  
  lines(c(opt_cap(-0.002512378,13.05937,10*48),opt_cap(-0.002512378,13.05937,10*48)),
        c(0,total_gain(opt_cap(-0.002512378,13.05937,10*48),10*48)),col = 3,lty = 2)
  lines(c(opt_cap(-0.002512378,13.05937,15*48),opt_cap(-0.002512378,13.05937,15*48)),
        c(0,total_gain(opt_cap(-0.002512378,13.05937,15*48),15*48)),col = 4,lty = 2)
  lines(c(opt_cap(-0.002512378,13.05937,20*48),opt_cap(-0.002512378,13.05937,20*48)),
        c(0,total_gain(opt_cap(-0.002512378,13.05937,20*48),20*48)),col = 5,lty = 2)
  
  lines(optimal_cap,optcost_cap/my,col = 6,lty = 3,lwd = 3)

legend(1400, 0.36*365, legend=c("p = 1","p = 5","p = 10","p = 15","p = 20","Maximum gain"),col=c(1, 2,3, 4,5,6), lty=c(1,1,1,1,1,3),lwd = 2.5, cex=0.75)
  dev.off()
```


```{r}
#plot Optimal capacity
#library(dplyr)
#data.byk1k2<-outpout_ab_p %>%group_split(V1,V2) 

cols <- 6:80 
optcapK2.1 <- colMeans(outpout_ab_p[1:3,cols]) #1：3 -> 2
optcapK2.2 <- colMeans(outpout_ab_p[4:6,cols])
optcapK2.3 <- colMeans(outpout_ab_p[7:9,cols])
optcapK2.4 <- colMeans(outpout_ab_p[10:12,cols])

pdf(file = paste0("figure_optcap_k1_",k2,".pdf"),height = 4.5, width = 5)
#par(oma=c(0,0,0,0),mar=c(5,5,2,2))
plot(seq(1,75,1),optcapK2.1,xlim = c(0,50), ylim=c(0,1700),xlab = "Battery cost (AUS $ per MV-30 mins)",ylab = "Optimal capacity (MV)",type = "l",col=1,lwd=2.5)

lines(seq(1,75,1),optcapK2.2,col=2,lwd=2.5)

lines(seq(1,75,1),optcapK2.3,col=3,lwd=2.5)
legend(30, 1500, legend=c(paste0("k1=400,","k2=",k2), paste0("k1=600,","k2=",k2),paste0("k1=800,","k2=",k2)),
       col=c(1, 2,3), lty=1,lwd = 2.5, cex=0.8)


dev.off()
```

```{r}
mypcost <- c(seq(0.1,0.9,by = 0.1)*48,pcost)

cols <- 4:5 
ab.1 <- colMeans(outpout_ab_p[1:3,cols]) #
ab.2 <- colMeans(outpout_ab_p[4:6,cols])
ab.3 <- colMeans(outpout_ab_p[7:9,cols])


optimal_cap1 <- opt_cap(ab.1[1],ab.1[2],mypcost) # k1=70,k2=400
optimal_cap1<-optimal_cap1[which(optimal_cap1>0)]
pcost_cap1 <- mypcost[which(optimal_cap1>0)]/48#seq(1,length(optimal_cap),by = 1)*48

optimal_cap2 <- opt_cap(ab.2[1],ab.2[2],mypcost) # k1=70,k2=400
optimal_cap2<-optimal_cap2[which(optimal_cap2>0)]
pcost_cap2 <- mypcost[which(optimal_cap2>0)]/48#seq(1,length(optimal_cap),by = 1)*48
optimal_cap3 <- opt_cap(ab.3[1],ab.3[2],mypcost) # k1=70,k2=400
optimal_cap3<-optimal_cap3[which(optimal_cap3>0)]
pcost_cap3 <- mypcost[which(optimal_cap3>0)]/48#seq(1,length(optimal_cap),by = 1)*48

pdf(file = paste0("figure_optcap_k1_",k2,".pdf"),height = 4.5, width = 5)
#par(oma=c(0,0,0,0),mar=c(5,5,2,2))
plot(pcost_cap1,optimal_cap1,xlim = c(0,45), ylim=c(0,2500),xlab = "Battery cost (AUS $ per MV-30 mins)",ylab = "Optimal capacity (MV)",type = "l",col=1,lwd=2.5)

lines(pcost_cap2, optimal_cap2,col=2,lwd=2.5)
lines(pcost_cap3, optimal_cap3,col=3,lwd=2.5)
legend(28, 1500, legend=c(paste0("k1=400,","k2=",k2), paste0("k1=600,","k2=",k2),paste0("k1=800,","k2=",k2)),
       col=c(1, 2,3), lty=1,lwd = 2.5, cex=0.8)


dev.off()
```


## Models without Battery

```{r}

#KK1 for over prediction and KK2 for under-prediction
MFC<-function(ERRS, KK1, KK2){
  
  k1 <- KK1/2
  k2 <- KK2/2
  
  PerCost<-ifelse(ERRS>0,k1*ERRS,k2*abs(ERRS))
  
  return(mean(PerCost)*48)
  
}
```

```{r}
#######################################
## epsilon-support vector regression###
#######################################

library(e1071)

SVRInputTrain<-cbind(XTrainCycle,InputTrain)

SVRInputTest<-cbind(XTestCycle, InputTest)

Basic_SVR<-svm(SVRInputTrain, OutputTrain, type = "eps-regression",scale = TRUE,kernel="linear")

Basic_SVR_Prediction<-predict(Basic_SVR, SVRInputTest)

Basic_SVR_Error<-Basic_SVR_Prediction-OutputTest

KK1 <- c(70,80,90)
KK2 <- c(400,600,800)
Basic_SVR_Error_cost <- matrix(0,3,3)
for(i in 1:3 ){
  for(j in 1:3){
   Basic_SVR_Error_cost[i,j]<- MFC(Basic_SVR_Error,KK1 = KK1[i],KK2 = KK2[j])

    
  }
}


```



```{r}
## LAV regression

library(L1pack)

LAV_TrainSet<-as.data.frame(cbind(XTrainCycle,InputTrain,OutputTrain))

Basic_LAV<-lad(formula = OutputTrain ~ ., data = LAV_TrainSet, method = "BR")

Basic_LAV_Prediction<-predict(Basic_LAV, newdata=as.data.frame(cbind(XTestCycle, InputTest)))

Basic_LAV_Error<-Basic_LAV_Prediction-OutputTest


KK1 <- c(70,80,90)
KK2 <- c(400,600,800)
Basic_LAV_Error_cost <- matrix(0,3,3)
for(i in 1:3 ){
  for(j in 1:3){
   Basic_LAV_Error_cost[i,j]<- MFC(Basic_LAV_Error,KK1 = KK1[i],KK2 = KK2[j])

    
  }
}


```
```{r}
#########################################
## Multilayer perception#################
#########################################

library(neuralnet)

maxs <- apply(LAV_TrainSet, 2, max)

mins <- apply(LAV_TrainSet, 2, min)

Scale_TrainSet <- as.data.frame(scale(LAV_TrainSet,center = mins, scale = maxs - mins))

Scale_TestSet <- as.data.frame(scale(cbind(XTestCycle,InputTest,OutputTest),center = mins, scale = maxs - mins))
names(Scale_TestSet)[51]<-"OutputTrain"

Basic_MLP<-neuralnet(formula = OutputTrain ~ .,Scale_TrainSet, hidden = 15, err.fct="sse",linear.output=TRUE,act.fct = "logistic")

Basic_MLP_Prediction <- compute(Basic_MLP, Scale_TestSet[,1:50])*(maxs[51]-mins[51])+mins[51]

Basic_MLP_Error<-Basic_MLP_Prediction-OutputTest





KK1 <- 80
KK2 <- 600
MFC(Basic_MLP_Error,KK1 = KK1,KK2 = KK2)
```

```{r}
###############################################
## Asymmetric LAV regression model training####
###############################################
AsyLAVStructure<-function(beta, TrainX, TrainY, k1,k2){
  
  beta<-array(beta)
  
  TrainX_extra=rep(1, times=dim(TrainX)[1])
  
  TrainX=cbind(TrainX_extra,TrainX)
  
  Xmatrix<-as.matrix(TrainX)
  
  Err<-Xmatrix %*% beta-TrainY
  
  # under-ordered, error cost k2, eps1
  Err1<- ifelse(Err < 0 ,-k2*(Err),0)

  # over-ordered, error cost k1, eps2,  
  Err2<- ifelse(Err > 0, k1*(Err), 0)
  
  SampleLLC<-Err1 + Err2
  
  TrainLLC<-sum(SampleLLC)
  
}
library(L1pack)

Scale_LAV<-lad(formula = OutputTrain ~ ., data = c.TrainSet, method = "BR")

Scale_Low_Limt<-rep(-1,51)

Scale_Upp_Limt<-rep(3,51)

k1<-80/2
k2<-800/2
#k<-k2/k1

Asy_LAV_Coef<-optim(as.array(Scale_LAV$coefficients), function(beta) 
  AsyLAVStructure(beta, c.TrainSet[,1:50], c.TrainSet[,51], k1, k2),
  method="L-BFGS-B")

Asy_LAV_Prediction<-as.matrix(cbind(rep(1, dim(c.TestSet)[1]),
                                          c.TestSet[,1:50]))%*% as.array(Asy_LAV_Coef$par)

Asy_LAV_Error<-Asy_LAV_Prediction-OutputTest

KK1 <- 80
KK2 <- 800
MFC(Asy_LAV_Error,KK1 = KK1,KK2 = KK2)



KK1 <- c(70,80,90)
KK2 <- c(400,600,800)
Asy_LAV_Error_cost <- matrix(0,3,3)

Asy_LAV_train_Error_cost <- matrix(0,3,3)


for(i in 1:3 ){
  for (j in 1:3) {
    
    k1 <- KK1[i] / 2
    k2 <- KK2[j] / 2
    Asy_LAV_Coef <-
      optim(as.array(Scale_LAV$coefficients), function(beta)
        AsyLAVStructure(beta, c.TrainSet[, 1:50], c.TrainSet[, 51], k1, k2),
        method = "L-BFGS-B")
    
    Asy_LAV_Prediction <- as.matrix(cbind(rep(1, dim(c.TestSet)[1]),
                                          c.TestSet[, 1:50])) %*% as.array(Asy_LAV_Coef$par)
    
    Asy_LAV_Error <- Asy_LAV_Prediction - OutputTest
    
    
    Asy_LAV_Error_cost[i, j] <-
      MFC(Asy_LAV_Error, KK1 = KK1[i], KK2 = KK2[j])
    
    Asy_LAV_Prediction_train <- as.matrix(cbind(rep(1, dim(c.TrainSet)[1]),
                                          c.TrainSet[, 1:50])) %*% as.array(Asy_LAV_Coef$par)
    
    Asy_LAV_Error_train <- Asy_LAV_Prediction_train - OutputTrain
    
    
    Asy_LAV_train_Error_cost[i, j] <-
      MFC(Asy_LAV_Error_train, KK1 = KK1[i], KK2 = KK2[j])
  }
}



```


```{r}
####################################################
###### Asymmetric SVR regression model training#####
####################################################

AsySVRStructure<-function(beta, TrainX, TrainY, k1, k2 , C, eps)
  
{
  
  beta<-array(beta)
  TrainX_extra=rep(1, times=dim(TrainX)[1])
  TrainX=cbind(TrainX_extra,TrainX)
  Xmatrix<-as.matrix(TrainX)
  Err<-Xmatrix %*% beta-TrainY
  
  # under-ordered, error cost k2, eps1
  InsenErr1<- ifelse(Err< -eps, -k2*(Err+eps),0)

  # over-ordered, error cost k1, eps2,  
  InsenErr2<- ifelse(Err> eps, k1*(Err-eps), 0)
  
  SampleLLC<- InsenErr1 + InsenErr2
  
  L2<-sum((beta[2:dim(TrainX)[2]])^2)
  
  TrainLLC<- L2+C*sum(SampleLLC)
  
}


KK1 <- c(70, 80, 90)
KK2 <- c(400, 600, 800)
Asy_SVR_Error_cost <- matrix(0, 3, 3)
Asy_SVR_Error_Train_cost <- matrix(0, 3, 3)


for (i in 1:3) {
  for (j in 1:3) {
    k1 <- KK1[i] / 2
    k2 <- KK2[j] / 2
    
    Asy_SVR_Coef <-
      optim(as.array(Scale_LAV$coefficients), function(beta)
        AsySVRStructure(
          beta,
          c.TrainSet[, 1:50],
          c.TrainSet[, 51],
          k1 = k1,
          k2 = k2,
          C = 10,
          eps = 0.001
        ),
        method = "L-BFGS-B")
    
    Asy_SVR_Prediction <- as.matrix(cbind(rep(1, dim(c.TestSet)[1]),
                                          c.TestSet[, 1:50])) %*% as.array(Asy_SVR_Coef$par)
    Asy_SVR_Error <- Asy_SVR_Prediction - OutputTest
    
    Asy_SVR_Error_cost[i, j] <-
      MFC(Asy_SVR_Error, KK1 = KK1[i], KK2 = KK2[j])
    
    
    
    Asy_SVR_train_Prediction <- as.matrix(cbind(rep(1, dim(c.TrainSet)[1]),
                                          c.TrainSet[, 1:50])) %*% as.array(Asy_SVR_Coef$par)
    Asy_SVR_train_Error <- Asy_SVR_train_Prediction - OutputTrain
    
    Asy_SVR_Error_Train_cost[i, j] <-
      MFC(Asy_SVR_train_Error, KK1 = KK1[i], KK2 = KK2[j])
    
  }
}

```
